Reviewer comments from PeerJ

### 2015-03-24 PeerJResponse.tex
edits to response

\res{We have editied the text to provide further clarification, page 8, lines 222-225: ``To investigate patterns of sequence diversity and linkage disequilibrium (LD) in the \emph{tb1} region and any evidence of selection on this locus, we sequenced two small ($<$1kb) regions upstream of the \emph{tb1} ORF in four populations from the Jalisco region."}

@@

\res{We have removed the comparisons made about the difference in frequencies of the \emph{Hopscotch} allele between ssp. \emph{parviglumis} and ssp. \emph{mexicana}.}

@@

\res{We sampled all individuals and populations that were available to us, which while it did not allow for even sample sizes across populations, did allow us to calculate \emph{Hopscotch} frequency in a subset of populations, as well as the geographic distribution of the \emph{Hopscotch} across many independent sampling locations. We have added a clarifying statement to the text regarding our sampling: page 4, lines 63-71: ``We sampled all individuals and populations that were available to us, consisting of 1,110 individuals from 350 populations (247 maize landraces, 17 \emph{mexicana} populations, and 86 \emph{parviglumis} populations) and assessed the presence or absence of the \emph{Hopscotch} insertion (Table S1 and Table S2, See Supplemental Materials with the online version of this article). Numbers of individuals sampled per population ranged from 1-43 for \emph{parviglumis}, 1-35 for \emph{mexicana}, and 1-18 for the maize landrace populations. Available samples did not allow us to sample evenly from populations, but did allow us to calculate \emph{Hopscotch} frequency in a subset of populations, as well as elucidate the geographic distribution of the \emph{Hopscotch} across multiple independent sampling sites."}

@@

\lev{I don't have access to this info. Can one of you guys help?}

\mbh{Jeff, can you help here?}

>>>>

\res{We have edited the text to provide further clarification, page 8, lines 222-225: ``To investigate patterns of sequence diversity and linkage disequilibrium (LD) in the \emph{tb1} region and any evidence of selection on this locus, we sequenced two small ($<$1kb) regions upstream of the \emph{tb1} ORF in four populations from the Jalisco region."}

@@

\res{The reviewer has made a valid point and we have removed the comparisons made about the difference in frequencies of the \emph{Hopscotch} allele between ssp. \emph{parviglumis} and ssp. \emph{mexicana}.}

@@

\res{We sampled all individuals and populations that were available to us, which, while it did not allow for even sample sizes across populations, did allow us to calculate \emph{Hopscotch} frequency in a subset of populations, as well as the geographic distribution of the \emph{Hopscotch} across many independent sampling locations. We have added a clarifying statement to the text regarding our sampling: page 4, lines 63-71: ``We sampled all individuals and populations that were available to us, consisting of 1,110 individuals from 350 populations (247 maize landraces, 17 \emph{mexicana} populations, and 86 \emph{parviglumis} populations) and assessed the presence or absence of the \emph{Hopscotch} insertion (Table S1 and Table S2, See Supplemental Materials with the online version of this article). Numbers of individuals sampled per population ranged from 1-43 for \emph{parviglumis}, 1-35 for \emph{mexicana}, and 1-18 for the maize landrace populations. Available samples did not allow us to sample evenly from populations, but did allow us to calculate \emph{Hopscotch} frequency in a subset of populations, as well as elucidate the geographic distribution of the \emph{Hopscotch} across multiple independent sampling sites."}

@@

\res{We have added this additional information to Supplemental Tables 1 and 2}
